\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Chengwen}
\familyname{Wang}
\title{Curriculum Vitae}
\mobile{+86 18042306511}
\email{hustwcw@qq.com}
%% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

%\phone{(312) 413-8265}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
\cventry{2011.09--Present}{MS in Middleware, Supervisor: Jianwei Yin}{School of Computer & Science, Huazhong University of Science & Technology}{expected 2014}{}{}
\cventry{2007.09--2011.06}{BA in Computer Science & Technology}{School of Computer & Science, Zhejiang University}{}{}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}
\section{Technology Skill}
\cventry{1}{}{}{}{}{}
\cventry{2}{}{}{}{}{}

\section{Internship}
\cventry{2012}{China Telecomt}{ECP Center}{}{}
{1.Develop the PaaS Open Platform for ECP. 2.Develop the iOS client of Yiliao. 3.Develop the server gateway for Yiliao.}
\cventry{2011}{Hangzhou JTang Infomation Technology co. , ltd}{}{}{}
{Develop the PC client of JTang UC(Union Communication) System.}

\section{Community}
\cventry{Blog}{\url{techblog.sinaapp.com}}{My blog (Chinese)}{}{}{}
%\cventry{Stack Overflow}{\url{stackoverflow.com/users/111896/zellux}}{Reputation top 4\%}{}{}{}
\cventry{GitHub}{\url{github.com/hustwcw}}{}{}{}{}

\section{Project Experience}
%% \subsection{Research Projects}

\cventry{2013.2--present}
{Enterprise Union Communication System}
{Windows PC Client}
{Enterprise Project}{}
{
An Enterprise-class communication system integrated with telephone, text messaging, instant messaging,
file transfer and address book management functions. My job is developing the PC client of this system.
}

\vspace*{0.2\baselineskip}
\cventry{2012.10--2013.2}
{China Telecom Yiliao Server Gateway}
{C/C++}
{Enterprise Project}{}
{
The project mainly to complete the load balancing service (judging by the IP address of the segment to achieve and by zookeeper), the new version of the communication protocol encryption compression library SIP gateway project. Through these projects more in-depth study of the C \ C + + programming, able to skillfully use the C language under Linux programming, familiar with C + + object-oriented programming.
}

\vspace*{0.2\baselineskip}
\cventry{2011.7--2012.10}
{China Telecom Yiliao iPhone Client}
{Objective-C}
{Enterprise Project}{}
{
Primarily responsible for the development of contacts and chat features, more in-depth study of the underlying network communication and project structure, and various other operations involving rich IOS development experience. Learning through the projects use Redmine and Git.
}

\vspace*{0.2\baselineskip}
\cventry{2011.3--2011.6}
{China Telecom ECP Open Platform}
{Java/PHP}
{Enterprise Project}{}
{
The project is a graduate design project, I am primarily responsible for the development of collaborative communications development platform communication interface structures Oauth 2.0 authorization protocol implementations, development platform wiki site.
}

\vspace*{0.2\baselineskip}
\cventry{2010.4--2010.5}
{Task Manager for Ubuntu}
{QT}
{Curriculum Design}{}
{
Desing and implement an task manager for ubuntu using QT independently. This application can view and manage
the system CPU, memory, network, process information  in a graphical way. This project makes me more familiar
with Linux programming environment, and cultivate the ability to learn new technologies quickly.
}

\vspace*{0.2\baselineskip}
\cventry{2010.9--2011.6}
{Samsung Bada application development}
{Bada C++}
{Sparetime Project}{}
{Participate in the first session of the Samsung bada application development contest, through which I first contact with mobile
application development. There 5 bada applications available for download in the Samsung App Store.
}

\vspace*{0.2\baselineskip}
\cventry{2010.7--2010.9}
{Desktop Visualization}
{C++}
{Research Project}{}
{The project's main work is send the server-side program interface to the client browser which use JavaScript to render the interface. 
Client user's operating events (mouse, keyboard, etc.) are then sent to the server-side, handled by the server-side application.
clientthrough the browser to use the functionality of the application server is running. Therefor, the client can use the
applications running in the server-side with a browser. I'm responsible for translating GDI & GDI+ API to Javascript graphic API.
}

\vspace*{0.2\baselineskip}
\cventry{2009.6--2010.4}
{}
{PHP, HTML, CSS, Javascript}
{Research Project}{}
{
Primarily responsible for site development background, through research, written the PRD document, develop, test and so on complete project process. I am primarily responsible for the development of the interactive part of the curriculum, including forums, Q & A, operations, and examinations. Project learning Web back-end and front-end development of knowledge, skilled PHP developers website background, website front-end development and use DIV + CSS. While practice software engineering courses learned knowledge.
}




%\section{Publications}

%\cventry{2012}
%{\textbf{Yuanxuan Wang}\textnormal{, Jincheng Han, Haibo Chen, Binyu Zang}}
%{ReDroid: Fast Malware Recovery on Smartphones with Intertwined Replay}{In IPADS Technique Report}
%{}{}{}

%\cventry{2011}
%{\textnormal{Xiang Song, Haibo Chen, Rong Chen,} \textbf{Yuanxuan Wang}\textnormal{, Binyu Zang}}
%{A Case for Scaling Applications to Many-core Platforms with OS Clustering}
%{In 2011 ACM SIGOPS European Conference on Computer Systems (Eurosys'2011)}
%{}{}{}

\section{Community Immersion}
\cventry{2011.9--Present}{CS Students' Union in ZJU}{}{}{}{}
\cventry{2008--2011}{Class Monitor}{}{}{}{}

\section{Awards}
\cventry{}{People's Scholarship}{3 times}{}{}{}
\cventry{}{University-level Outstanding Student Leader}{twice}{}{}{}
\cventry{2008.5}{Software Developer Certificate}{}{}{}{}


\section{English Skill}
\cventry{CET-6}{587}{}{}{}{}
\cventry{CET-4}{601}{}{}{}{}
\cventry{}{Good at listening and speaking, capable of using it as working language}{}{}{}{}
% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

\end{document}
